TINET+TECS: Component-based TCP/IP Protocol Stack for Embedded Systems

### 2017-02-11 ISORC2017/diff/20170208.tex
Add the tex file at 2017/02/08

\begin{table}[t]
    \centering
    \caption{Memory consumption of TINET and TINET+TECS}
    \begin{tabular}{c|r|r|r|r}
        \hline\hline
                    &   text       &  data    &   bss      &  total     \\ \hline
        TINET       &   183.94 KB  &  5.37 KB &  132.03 KB &  322.34 KB \\
        TINET+TECS  &   170.73 KB  &  5.37 KB &  149.13 KB &  325.23 KB \\
        \hline
        \multicolumn{5}{r}{Including the application and kernel objects}
    \end{tabular}
    \label{tab:EvaluationOfMemoryConsumption}
\end{table}

@@

\begin{table}[t]
    \centering
    \caption{Modified code lines of CDL}
    \begin{tabular}{c|r|r|r}
        \hline\hline
                         &   Size       &   Size (- Default)  & CDL  \\ \hline
        Default          &   325.23 KB  &             0 KB    &  0 lines   \\
        I                &   305.40 KB  &       - 19.83 KB    & 18 lines    \\
        I + I\hspace{-.1em}I &   304.12 KB  &   - 21.10 KB    & 27 lines   \\
        I + I\hspace{-.1em}I + I\hspace{-.1em}I\hspace{-.1em}I & 303.45 KB & - 21.77 KB  & 32 lines \\
        \hline
        \multicolumn{4}{l}{I: Remove TCP}\\
        \multicolumn{4}{l}{I\hspace{-.1em}I: Remove ICMP}\\
        \multicolumn{4}{l}{I\hspace{-.1em}I\hspace{-.1em}I: Change network buffer (Remove memory pools)}
    \end{tabular}
    \label{tab:EvaluationOfConfigurability}
\end{table}

@@

\begin{table}[t]
    \centering
    \caption{CDL code lines of without/with dynamic connection}
    \begin{tabular}{l|r|r|r}
        \hline\hline
                     &  without  &  with  &  Diff  \\ \hline
        CEP:1 REP:1  &  344 lines     &  347 lines  &  -3 lines   \\
        CEP:1 REP:5  &  369 lines     &  367 lines  &   2 lines   \\
        CEP:2 REP:5  &  387 lines     &  382 lines  &   5 lines   \\
        CEP:5 REP:10 &  485 lines     &  445 lines  &  40 lines   \\
        \hline
    \end{tabular}
    \label{tab:EvaluationOfConfigurabilityByDynamicConnection}
\end{table}

\begin{figure}[t]
 \centering
 \begin{lstlisting}
/* without Dynamic Connection */
cell tTCPCEP TCPCEP_000 {
    cREP[0] = REP_000.eREP;
    ..
    cREP[n] = REP_00n.eREP;
};
cell tTCPCEP TCPCEP_001 {
    cREP[0] = REP_000.eREP;
    ..
    cREP[n] = REP_00n.eREP;
};
..
cell tTCPCEP TCPCEP_00n {
    cREP[0] = REP_000.eREP;
    ..
    cREP[n] = REP_00n.eREP;
};
 \end{lstlisting}
 \centering
 \begin{lstlisting}
/* with Dynamic Connection */
cell tRepSelector RepSelector {
    cREP[0] = REP_000.eREP;
    ..
    cREP[n] = REP_00n.eREP;
};
cell tTCPCEP TCPCEP_000 {
    cRepSelector = RepSelector.eRepSelector;
};
cell tTCPCEP TCPCEP_001 {
    cRepSelector = RepSelector.eRepSelector;
};
..
cell tTCPCEP TCPCEP_00n {
    cRepSelector = RepSelector.eRepSelector;
};
 \end{lstlisting}
 \caption{Comparison of CDL descriptions between without/with dynamic connection}
 \label{src:ComparisonOfCDL}
\end{figure}

The comparison of CDL code lines of without/with dynamic connection is shown in TABLE \ref{tab:EvaluationOfConfigurabilityByDynamicConnection}, to demonstrate improved configurability by dynamic connection.
As the number of CEPs and REPs increases, the amount of CDL code lines to be added increases.
In the left part of Fig. \ref{fig:ComparisonOfDynamicConnection}, each CEP connects all REPs as shown in the upper of Fig. \ref{src:ComparisonOfCDL}. 
In the right part of Fig. \ref{fig:ComparisonOfDynamicConnection}, a CEP dynamically connects an REP, and only the selector connects all REPs as shown in the lower of Fig. \ref{src:ComparisonOfCDL}. 
Since the difference spreads as the number of CEPs and REPs increases, it is effective for software that uses many ports.

>>>>

\begin{table}[t]
    \centering
    \caption{Memory consumption of TINET and TINET+TECS}
    \begin{tabular}{c|r|r}
        \hline\hline
                  &   TINET      &   TINET+TECS  \\ \hline
        ROM       &   74.93 KB   &   76.62 KB   \\
        RAM       &   27.36 KB   &   28.24 KB   \\
        ROM + RAM &   102.29 KB  &   103.86 KB   \\
        \hline
    \end{tabular}
    \label{tab:EvaluationOfMemoryConsumption}
\end{table}

@@

\begin{table}[t]
    \centering
    \caption{Modified code lines of CDL}
    \begin{tabular}{c|r|r|r}
        \hline\hline
                         &   Size       &   Size (- Default)  & CDL  \\ \hline
        Default          &   104.86 KB  &   0 KB           & 0    \\
        I                &   80.79 KB   &   - 24.07 KB     & 18    \\
        I + I\hspace{-.1em}I &   80.50 KB  &   - 26.35 KB  & 26    \\
        I + I\hspace{-.1em}I + I\hspace{-.1em}I\hspace{-.1em}I   & 72.03 KB & - 32.83 KB  & 31 \\
        \hline
    \end{tabular}
    \label{tab:EvaluationOfConfigurability}
\end{table}

@@
